`r paste(params$species)` biomass trends and figures

### 2019-12-05 analysis/VOCC/3-bioclimatic-trends.Rmd
start drafting addition of 2011 cutoff and tv depth option

---
title: "`r paste(params$species)` biomass trends and figures"
author: "Philina English"
date: "`r Sys.Date()`"
output: html_document
params: 
    #species: "Pacific Cod" # 
    species: "Redbanded Rockfish"
    region: "All synoptic surveys"
    start_year: 2008
    bind_predictions: FALSE
    covs: "-all" 
    # year_cutoff: 2012
    #covs: "-log-both-fixed-depth"
    #covs: "-log-both-noAR1" # covariate string used to name model rds 
---

@@

  adult_biomass <- readRDS(paste0("data/", spp, 
        "/mod-mat-biomass-", spp,"-fixed", covs, "--", ssid_string, "-prior-", priors, ".rds"))
  #nd$year <- as.integer(nd$year)

@@

  nd_pre_2013 <- nd %>% filter(year < 2013)
  ad_model_2013 <- readRDS(paste0("data/", spp, 
        "/mod-mat-biomass-", spp,"-fixed-past-2013-", ssid_string, "-prior-", priors, ".rds"))
  adult_pre_2013 <- predict(ad_model_2013, newdata = nd_pre_2013, return_tmb_object = TRUE)

@@

  nd_pre_2015 <- nd %>% filter(year < 2015)
  ad_model_2015 <- readRDS(paste0("data/", spp, 
        "/mod-mat-biomass-", spp,"-fixed-past-2015-", ssid_string, "-prior-", priors, ".rds"))
  adult_pre_2015 <- predict(ad_model_2015, newdata = nd_pre_2015, return_tmb_object = TRUE)

@@

  nd_pre_2017 <- nd %>% filter(year < 2017)
  ad_model_2017 <- readRDS(paste0("data/", spp, 
        "/mod-mat-biomass-", spp,"-fixed-past-2017-", ssid_string, "-prior-", priors, ".rds"))
  adult_pre_2017 <- predict(ad_model_2017, newdata = nd_pre_2017, return_tmb_object = TRUE)

@@

  fake_2017_minus4 <- nd %>% 
    mutate(year = year - 4) %>% 
    filter(year > 2007)
  sort(unique(fake_2017_minus4$year))
  adult_2017_multi <- predict(ad_model_past, newdata = fake_2017_minus4, return_tmb_object = TRUE)
  adult_2017_multi$data$year <- adult_2017_multi$data$year + 4
  sort(unique(adult_2017_multi$data$year))

@@

   bioclim_2013_start <- filter(adult_pre_2013$data, year >= 2011) %>% filter(year <= 2012) %>%
    mutate(bioclim_2013 = est)
  bioclim_2013_end <- filter(adult_2013$data, year >= 2013) %>% filter(year <= 2014) %>%
    mutate(bioclim_2013 = est_non_rf + omega_s)
  bioclim_2013 <- dplyr::bind_rows(bioclim_2013_start, bioclim_2013_end)

  bioclim_2015_start <- filter(adult_past$data, year >= 2013) %>% filter(year <= 2014) %>%
    mutate(bioclim_2015 = est) %>% select(X,Y, year, bioclim_2015)
  bioclim_2013 <- left_join(bioclim_2013, bioclim_2015_start) %>% 
    select(X,Y, year, bioclim_2013, bioclim_2015)
  past_predictions <- left_join(past_predictions, bioclim_2013)

  bioclim_2015 <- filter(adult_2015$data, year >= 2015) %>% filter(year <= 2016) %>%
    mutate(blob_bioclim = est_non_rf + omega_s, bioclim_2015 = est_non_rf + omega_s)

@@

>>>>

---
title: "`r paste(params$species)` biomass trends and figures"
author: "Philina English"
date: "`r Sys.Date()`"
output: html_document
params: 
    #species: "Pacific Cod" # 
    species: "Redbanded Rockfish"
    region: "All synoptic surveys"
    start_year: 2008
    bind_predictions: FALSE
    covs: "-fixed"  
    # year_cutoff: 2012
    #covs: "-log-both-fixed-depth"
    #covs: "-log-both-noAR1" # covariate string used to name model rds 
---

@@

  adult_biomass <- readRDS(paste0("data/", spp, 
        "/mod-mat-biomass-", spp, covs, "-all--", ssid_string, "-prior-", priors, ".rds"))
  #nd$year <- as.integer(nd$year)

@@

  # nd_pre_2011 <- nd %>% filter(year < 2011)
  # ad_model_2011 <- readRDS(paste0("data/", spp,
  #       "/mod-mat-biomass-", spp, covs,"-past-2011-", ssid_string, "-prior-", priors, ".rds"))
  # sort(unique(ad_model_2011$data$year))
  # adult_pre_2011 <- predict(ad_model_2011, newdata = nd_pre_2011, return_tmb_object = TRUE)
  # 
  # fake_2011 <- nd %>%
  #   mutate(year = year - 2) %>%
  #   filter(year > 2007) %>% filter(year < 2011 )
  # sort(unique(fake_2011$year))
  # sort(unique(nd_pre_2011$year))
  # adult_2011 <- predict(ad_model_2011, newdata = fake_2011, return_tmb_object = TRUE)
  # adult_2011$data$year <- adult_2011$data$year + 2

  nd_pre_2013 <- nd %>% filter(year < 2013)
  ad_model_2013 <- readRDS(paste0("data/", spp, 
        "/mod-mat-biomass-", spp, covs,"-past-2013-", ssid_string, "-prior-", priors, ".rds"))
  adult_pre_2013 <- predict(ad_model_2013, newdata = nd_pre_2013, return_tmb_object = TRUE)

@@

  nd_pre_2015 <- nd %>% filter(year < 2015)
  ad_model_2015 <- readRDS(paste0("data/", spp, 
        "/mod-mat-biomass-", spp, covs,"-past-2015-", ssid_string, "-prior-", priors, ".rds"))
  adult_pre_2015 <- predict(ad_model_2015, newdata = nd_pre_2015, return_tmb_object = TRUE)

@@

  nd_pre_2017 <- nd %>% filter(year < 2017)
  ad_model_2017 <- readRDS(paste0("data/", spp, 
        "/mod-mat-biomass-", spp, covs,"-past-2017-", ssid_string, "-prior-", priors, ".rds"))
  adult_pre_2017 <- predict(ad_model_2017, newdata = nd_pre_2017, return_tmb_object = TRUE)

@@

  fake_2017_minus4 <- nd %>% 
    mutate(year = year - 4) %>% 
    filter(year > 2007)
  sort(unique(fake_2017_minus4$year))
  sort(unique(nd_pre_2015$year))
  adult_2017_multi <- predict(ad_model_2015, newdata = fake_2017_minus4, return_tmb_object = TRUE)
  adult_2017_multi$data$year <- adult_2017_multi$data$year + 4
  sort(unique(adult_2017_multi$data$year))

@@

  # bioclim_2011_start <- filter(adult_pre_2011$data, year >= 2009) %>% filter(year <= 2010) %>%
  #   mutate(bioclim_2011 = est)
  # bioclim_2011_end <- filter(adult_2013$data, year >= 2011) %>% filter(year <= 2012) %>%
  #   mutate(bioclim_2011 = est_non_rf + omega_s)
  # bioclim_2011_all <- dplyr::bind_rows(bioclim_2011_start, bioclim_2011_end)

  bioclim_2013_start <- filter(adult_pre_2013$data, year >= 2011) %>% filter(year <= 2012) %>%
    mutate(bioclim_2013 = est) #%>% select(X,Y, year, bioclim_2013)
  # bioclim_2013_all <- left_join(bioclim_2011, bioclim_2013_start) %>% 
  #   select(X,Y, year, bioclim_2011, bioclim_2013)
  #past_predictions <- left_join(past_predictions, bioclim_2011_all)

  bioclim_2013_end <- filter(adult_2013$data, year >= 2013) %>% filter(year <= 2014) %>%
    mutate(bioclim_2013 = est_non_rf + omega_s)

  bioclim_2013_all <- dplyr::bind_rows(bioclim_2013_start, bioclim_2013_end)

  bioclim_2015_start <- filter(adult_2015$data, year >= 2013) %>% filter(year <= 2014) %>%
    mutate(bioclim_2015 = est) %>% 
    select(X,Y, year, bioclim_2015)

  bioclim_2013_all <- left_join(bioclim_2013_all, bioclim_2015_start) %>% 
    select(X,Y, year, bioclim_2013, bioclim_2015)
  past_predictions <- left_join(past_predictions, bioclim_2013_all)

  bioclim_2015_end <- filter(adult_2015$data, year >= 2015) %>% filter(year <= 2016) %>%
    mutate(blob_bioclim = est_non_rf + omega_s, bioclim_2015 = est_non_rf + omega_s)

@@

  bioclim_2015 <- left_join(bioclim_2015_end, bioclim_2017_start)
